A Global Picture of Food Insecurity and Hunger

### 2020-09-09 docs/modeling_fies.tex
Updates from Overleaf

Globally, in the year 2020, we estimate that 2.33 billion people experience at least moderate food insecurity, and 829 million people experience severe food insecurity (See Fig. \ref{fig:timeseries}).  While the total number of people in moderate and severe food security held roughly constant for the 2010s and even increased in latter part of that decade, we predict that it will decline throughout the 2020s.  However, this overall decline will not be uniform across the world.  Our model expects that, in sub-Saharan Africa, moderate food insecurity will increase throughout the 2020s and severe food insecurity will plateau.  Food Security will fall in most other world regions, particularly South Asia and East Asia \& the Pacific.

@@

@@

Random Forest

Hyperparameter selection

>>>>

Globally, in the year 2020, we estimate that 2.33 billion people experience at least moderate food insecurity, and 829 million people experience severe food insecurity (See Fig. \ref{fig:timeseries}).  While the total number of people in moderate and severe food security held roughly constant for the 2010s and even increased in latter part of that decade, we predict that it will decline throughout the 2020s.  However, this overall decline will not be uniform across the world.  Our model expects that, in sub-Saharan Africa, moderate food insecurity will increase throughout the 2020s and severe food insecurity will plateau, although it will improve in some countries, such as Kenya, Senegal, and Ethiopia.  Food Security will fall in most other world regions, particularly South Asia and East Asia \& the Pacific.

@@

Dynamics of population growth and development

Deal with scale - why modeling at admin1 is a different exercise than local level modeling

What is driving the increases?
What will drive the decreases? (caveats of RF method)

@@

- tried different modelling approaches: lasso, bayes ssvs and random forest

- random forest performed best in terms of r2/mse and predictions

- random forest used because it captures interactions, machine learning approach

- tuned hyperparameters based on OOB error rate for different combinations, mtry and nodesize

- estimated 5000 trees

- awesome in-sample fit, overfitting?

- out-of-sample fit also very good, r2 around 0.99

- variable importance and coefficient table?
